\documentclass[11pt, margin, line]{res}


%Adjust margins
\topmargin=-.5in
\addtolength{\textwidth}{1in}
\addtolength{\resumewidth}{1in}
\addtolength{\textheight}{1in}
\addtolength{\oddsidemargin}{-.5in}
\addtolength{\evensidemargin}{-.5in}


\usepackage{fontspec}
\setmainfont{FreeSerif}

\usepackage{enumitem}
\renewcommand{\labelitemii}{\char"25E6}
\setlist[itemize]{itemsep=-3pt}

\usepackage{hyperref}


\name{\huge\bf Alexander Kursell}
\email{awkursel@uwaterloo.ca}
\phone{(416) 707-0391}
\site{\url{https://github.com/alexkursell}}
\address{ }


\begin{document}
\begin{resume}
 
\vspace{-1.5\topsep}
\section{SUMMARY OF \\ QUALIFICATIONS}   
    \begin{itemize}
        \item Six years of experience using \textbf{Python}.
        \item One to two years experience in \textbf{C, Javascript, Java, and LaTeX}.
        \item Three months of experience using \textbf{Rust}.
        \item Three years experience in high-traffic retail position. Non-technical, but with a heavy emphasis on soft skills and working without close supervision.
    \end{itemize}

\section{PROJECTS /\\ COMPETITIONS}
    \dateditem{ScrapeSave - Firefox Page Scraping Extension}{March 2017 - June 2017}
        \vspace{-\topsep}
        \begin{itemize}
            \item Implemented in \textbf{Javascript} and \textbf{jQuery}, along with \textbf{HTML} and \textbf{CSS} for the interface.
            \item Scrapes and collates arbitrary sections of multiple similar pages into a single HTML file.
            \item Use cases: Retrieving all articles of a blog, all pages of a webcomic, series of Reddit posts.
        \end{itemize}
    
    \dateditem{AlexChat - Serverless Graphical Chat Client}{November 2016 - January 2017}
        \vspace{-\topsep}
        \begin{itemize}
            \item Implemented in \textbf{Python} using only components of the standard library.
            \item Uses TCP and UDP sockets to discover and communicate with peers on the same network.
            \item Requires no configuration, setup, installation, or peer bootstrapping.
        \end{itemize}
    
    \dateditem{Programming Competitions}{}
        \vspace{-\topsep}
        \begin{itemize}
            \item Recieved Distinction (top 25\%) in the 2017 Canadian Computing Competition (CCC).
            \item Recieved Distinction (top 25\%) in the 2017 Euclid math competition.
            \item Team reached and placed in the top 10 in the final, province-wide round of the 2017 Educational Computing Organization of Ontario contest (ECOO).
        \end{itemize}



\section{WORK /\\ LEADERSHIP} 
    \dateditem{President}{September 2016 - June 2017}
        Thornhill Secondary School Computer Club
        \begin{itemize}
            \item Taught large (20+ people) introductory programming classes in Python for new members.
            \item Planned and managed club trips with attendances from 8 - 12 people.
            \item Handled club funding requests, writing field trip consent forms, other required paperwork.
        \end{itemize}

    \dateditem{Retail Sales Associate}{February 2015 - August 2017}
        Cedar Fair Entertainment Company, \\
        Canada's Wonderland Merchandise Department, Vaughan, ON 
        \begin{itemize}
            \item Sucessfully operated retail location alone with infrequent contact with supervisor.
            \item Served many customers at once, often within high-traffic periods.
            \item Worked long (8-12 hr) shifts through weekends while school was still running, full time in summer.
            \item Recieved multiple positive performance reviews. Supervisor references available upon request.
        \end{itemize}
  
            


\section{EDUCATION} 
    \dateditem{Candidate for Bachelor of Software Engineering}{September 2017 - present}
        Honours Software Engineering, \\
        University of Waterloo, Waterloo, ON
        \begin{itemize}
            \item First term average of 95\%.
        \end{itemize}

    \dateditem{High School Diploma}{June 2017}
        Thornhill Secondary School, Thornhill, ON
        \begin{itemize}
            \item Grade 12 average mark of 96.5\%.
            \item Highest mark in class in 3 of 7 grade 12 classes.
        \end{itemize}


\end{resume}
\end{document}




